Paper 1

### 2022-08-01 scripts/Paper 1.Rmd
add detailed seasons, remove scale_color_manual(need to put new in with new year)

```{r create daily mean dataframe, include=FALSE}
# add variables to this daily df as needed
input.daily <- input %>%
  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
  ddply(c("Year", "jday", "month"), summarise,
        Precip = sum(Precip, na.rm = TRUE),
        SWin = sum(SWin),
        Ta.mean = mean(Ta, na.rm = TRUE),
        Ta.max = max(Ta, na.rm = TRUE),
        Ta.min = min(Ta, na.rm = TRUE),
        Ts.mean = mean(Ts, na.rm = TRUE),
        Ts.max = max(Ts, na.rm = TRUE),
        Ts.min = min(Ts, na.rm = TRUE),
        SWC = mean(SWC, na.rm = TRUE),
        RH = mean(RH, na.rm = TRUE),
        VPD = mean(VPD, na.rm = TRUE),
        ET = mean(ET, na.rm = TRUE)* 86400,#daily total ET
        NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1
        ER_LT = mean(ER_LT, na.rm = TRUE),
        GPP_LT = mean(GPP_LT, na.rm = TRUE)) %>%
  mutate(NEE_LT.gC = gofC.f(NEE_LT),  #converts to daily total NEE in g C CO2
         ER_LT.gC = gofC.f(ER_LT),
         GPP_LT.gC = gofC.f(GPP_LT))

@@

Grow21.22 <- input.daily[530:907,]
Grow21.22$dayssinceJun1 <-1:378
Grow21.22$GSYear <- "21/22"

input.rearranged <- rbind(Grow19.20,Grow20.21, Grow21.22)
input.rearranged$monthyear <- as.yearmon(paste(input.rearranged$month, input.rearranged$Year), "%m %Y")

@@

```{r}
input.rearranged$season <- "" # add season variable

# define seasons
winter <- (input.rearranged$month.name == "Jun" | input.rearranged$month.name == "Jul" | input.rearranged$month.name == "Aug")
spring <- (input.rearranged$month.name == "Sep" | input.rearranged$month.name == "Oct" | input.rearranged$month.name == "Nov")
summer <- (input.rearranged$month.name == "Dec" | input.rearranged$month.name == "Jan" | input.rearranged$month.name == "Feb")
autumn <- (input.rearranged$month.name == "Mar" | input.rearranged$month.name == "Apr" | input.rearranged$month.name == "May")

input.rearranged$season[winter] <- "Winter"
input.rearranged$season[spring] <- "Spring"
input.rearranged$season[summer] <- "Summer"
#input.rearranged$season[latesummer] <- "LateSummer"
input.rearranged$season[autumn] <- "Autumn"

input.rearranged$season <- factor(input.rearranged$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
```

@@

# define seasons
winter <- (rainfall_L$month.name == "Jun" | rainfall_L$month.name == "Jul" | rainfall_L$month.name == "Aug")
spring <- (rainfall_L$month.name == "Sep" | rainfall_L$month.name == "Oct" | rainfall_L$month.name == "Nov")
summer <- (rainfall_L$month.name == "Dec" | rainfall_L$month.name == "Jan" | rainfall_L$month.name == "Feb")
autumn <- (rainfall_L$month.name == "Mar" | rainfall_L$month.name == "Apr" | rainfall_L$month.name == "May")

rainfall_L$season[winter] <- "Winter"
rainfall_L$season[spring] <- "Spring"
rainfall_L$season[summer] <- "Summer"
rainfall_L$season[autumn] <- "Autumn"

rainfall_L$season <- factor(rainfall_L$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
```

```{r, fig.width=11, fig.height=4}
season.colors <- c("Summer" = "#E69F00", "Autumn" = "#D55E00", "Winter" ="#0072B2", "Spring" = "#CC79A7")

rainfall.SP <- input.rearranged %>% select(Precip, month, GSYear, season, Year, month.name)

rainfall <- rainfall_L %>% select(Precip, month, GSYear, season, Year, month.name) %>% rbind(., rainfall.SP)

@@

(rainfall.season <- rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("GSYear", "season"), summarise,
  seasonal.total = sum(Precip)) %>%
  ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
       #scale_x_discrete(limits = month.abb) +
  geom_col(aes(fill = season)) +
        scale_fill_manual(values = season.colors)+
  ylab("Seasonal rainfall (mm)")+
  xlab("Growing season year")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

@@

rainfall.summary <- rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("GSYear", "season"), summarise,
  seasonal.total = sum(Precip))
```

>>>>

```{r create daily mean dataframe, include=FALSE}
# add variables to this daily df as needed
input.daily <- input %>%
  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
  ddply(c("Year", "jday", "month"), summarise,
        Precip = sum(Precip, na.rm = TRUE),
        SWin = sum(SWin, na.rm=TRUE),
        Ta.mean = mean(Ta, na.rm = TRUE),
        Ta.max = max(Ta, na.rm = TRUE),
        Ta.min = min(Ta, na.rm = TRUE),
        Ts.mean = mean(Ts, na.rm = TRUE),
        Ts.max = max(Ts, na.rm = TRUE),
        Ts.min = min(Ts, na.rm = TRUE),
        SWC = mean(SWC, na.rm = TRUE),
        RH = mean(RH, na.rm = TRUE),
        VPD = mean(VPD, na.rm = TRUE),
        ET = mean(ET, na.rm = TRUE)* 86400,#daily total ET
        NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1
        ER_LT = mean(ER_LT, na.rm = TRUE),
        GPP_LT = mean(GPP_LT, na.rm = TRUE)) %>%
  mutate(NEE_LT.gC = gofC.f(NEE_LT),  #converts to daily total NEE in g C CO2
         ER_LT.gC = gofC.f(ER_LT),
         GPP_LT.gC = gofC.f(GPP_LT))

@@

Grow21.22 <- input.daily[530:894,]
Grow21.22$dayssinceJun1 <-1:365
Grow21.22$GSYear <- "21/22"

Grow22.23 <- input.daily[895:945,]
Grow22.23$dayssinceJun1 <-1:51
Grow22.23$GSYear <- "22/23"

input.rearranged <- rbind(Grow19.20,Grow20.21, Grow21.22, Grow22.23)
input.rearranged$monthyear <- as.yearmon(paste(input.rearranged$month, input.rearranged$Year), "%m %Y")

@@

```{r}
#input.rearranged$season <- "" # add season variable

# define seasons
#winter <- (input.rearranged$month.name == "Jun" | input.rearranged$month.name == "Jul" | input.rearranged$month.name == "Aug")
#spring <- (input.rearranged$month.name == "Sep" | input.rearranged$month.name == "Oct" | input.rearranged$month.name == "Nov")
#summer <- (input.rearranged$month.name == "Dec" | input.rearranged$month.name == "Jan" | input.rearranged$month.name == "Feb")
#autumn <- (input.rearranged$month.name == "Mar" | input.rearranged$month.name == "Apr" | input.rearranged$month.name == "May")

#input.rearranged$season[winter] <- "Winter"
#input.rearranged$season[spring] <- "Spring"
#input.rearranged$season[summer] <- "Summer"
#input.rearranged$season[latesummer] <- "LateSummer"
#input.rearranged$season[autumn] <- "Autumn"

#input.rearranged$season <- factor(input.rearranged$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
```

```{r six seasons}
#This needs better confines - e.g. month where temps are > or < something

input.rearranged$season.detail <- "" # add season variable

# define seasons
earlywinter <- (input.rearranged$month.name == "Jun" | input.rearranged$month.name == "May")
latewinter <- (input.rearranged$month.name == "Jul" | input.rearranged$month.name == "Aug")
spring <- (input.rearranged$month.name == "Sep" | input.rearranged$month.name == "Oct")
earlysummer <- (input.rearranged$month.name == "Dec" | input.rearranged$month.name == "Nov")
latesummer <- (input.rearranged$month.name == "Jan" | input.rearranged$month.name == "Feb")
autumn <- (input.rearranged$month.name == "Mar" | input.rearranged$month.name == "Apr")

input.rearranged$season.detail[latewinter] <- "LateWinter"
input.rearranged$season.detail[earlywinter] <- "EarlyWinter"
input.rearranged$season.detail[spring] <- "Spring"
input.rearranged$season.detail[earlysummer] <- "EarlySummer"
input.rearranged$season.detail[latesummer] <- "LateSummer"
input.rearranged$season.detail[autumn] <- "Autumn"

input.rearranged$season.detail <- factor(input.rearranged$season , levels=c('EarlySummer', 'LateSummer', 'Autumn', 'EarlyWinter', 'LateWinter', 'Spring'))
```

@@

# define seasons
#winter <- (rainfall_L$month.name == "Jun" | rainfall_L$month.name == "Jul" | rainfall_L$month.name == "Aug")
#spring <- (rainfall_L$month.name == "Sep" | rainfall_L$month.name == "Oct" | rainfall_L$month.name == "Nov")
#summer <- (rainfall_L$month.name == "Dec" | rainfall_L$month.name == "Jan" | rainfall_L$month.name == "Feb")
#autumn <- (rainfall_L$month.name == "Mar" | rainfall_L$month.name == "Apr" | rainfall_L$month.name == "May")

#rainfall_L$season[winter] <- "Winter"
#rainfall_L$season[spring] <- "Spring"
#rainfall_L$season[summer] <- "Summer"
#rainfall_L$season[autumn] <- "Autumn"

#rainfall_L$season <- factor(rainfall_L$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))

# define seasons
earlywinter <- (rainfall_L$month.name == "Jun" | rainfall_L$month.name == "May")
latewinter <- (rainfall_L$month.name == "Jul" | rainfall_L$month.name == "Aug")
spring <- (rainfall_L$month.name == "Sep" | rainfall_L$month.name == "Oct")
earlysummer <- (rainfall_L$month.name == "Dec" | rainfall_L$month.name == "Nov")
latesummer <- (rainfall_L$month.name == "Jan" | rainfall_L$month.name == "Feb")
autumn <- (rainfall_L$month.name == "Mar" | rainfall_L$month.name == "Apr")

rainfall_L$season.detail[latewinter] <- "LateWinter"
rainfall_L$season.detail[earlywinter] <- "EarlyWinter"
rainfall_L$season.detail[spring] <- "Spring"
rainfall_L$season.detail[earlysummer] <- "EarlySummer"
rainfall_L$season.detail[latesummer] <- "LateSummer"
rainfall_L$season.detail[autumn] <- "Autumn"

rainfall_L$season.detail <- factor(rainfall_L$season , levels=c('EarlyWinter', 'LateWinter', 'Spring', "EarlySummer", "LateSummer", "Autumn"))
```

```{r, fig.width=11, fig.height=4}
#season.colors <- c("Summer" = "#E69F00", "Autumn" = "#D55E00", "Winter" ="#0072B2", "Spring" = "#CC79A7")

rainfall.SP <- input.rearranged %>% select(Precip, month, GSYear, season.detail, Year, month.name)

rainfall <- rainfall_L %>% select(Precip, month, GSYear, season.detail, Year, month.name) %>% rbind(., rainfall.SP)

@@

(rainfall.season <- rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("GSYear", "season.detail"), summarise,
  seasonal.total = sum(Precip)) %>%
  ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season.detail)) +
       #scale_x_discrete(limits = month.abb) +
  geom_col(aes(fill = season.detail)) +
        #scale_fill_manual(values = season.colors)+
  ylab("Seasonal rainfall (mm)")+
  xlab("Growing season year")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

@@

rainfall.summary <- rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("GSYear", "season.detail"), summarise,
  seasonal.total = sum(Precip))
```
